---
title: "Compare with Benchmarks"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Compare with Benchmarks}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(uxr)
```

The `compare_benchmark_*` functions provide ways to compare benchmark with data like events and times. 

Events are outcomes of things that happen. For example, 10 out of 14 people successfully completed a task on an interface. We would like to know if this success rate can be above a certain threshold, let's say 80%. First we can calculate the success rate which is 10/14 = 0.84 (or 84%). Now the function takes the binomial probability of this and returns a probability value. We sum all the event probabilities and return a composite score. This is an estimate of how things might turn out if we were to implement this interface.

```{r}
compare_benchmark_event(benchmark = 0.80,
                        event = 10,
                        total = 12,
                        event_type = "success",
                        notes = "executive")
```

