---
title: "Compare with Benchmarks"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Compare with Benchmarks}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```



The `compare_benchmark_*` functions provide ways to compare benchmark with data like events and times. 


## Compare an Event with a Benchmark

**Note**: This function is not yet released. You need to install the development version to use this function. To install the developmental version enter this in your console: `remotes::install_github("joe-chelladurai/uxr")`. 

An event is "a thing that happens" (Oxford Learner's Dictionary).

**Example:**

10 out of 14 people successfully completed a task on an interface. What is the probability of success above a benchmark of 80%? 

You can use the `compare_benchmark_event()` function to answer this question. This function requires a benchmark value, number of events (in this case successful events), and the total number of events. To pass a `benchmark` value of 80%, you'll need to specify it as 0.8. The `event` and `total` arguments each take numeric values 1 or above.

The function calculates the success rates and returns a cumulative probability value against the benchmark. This probability value indicates the success rate  if we were to use this interface with potential users, given a representative sample.

```{r setup, echo = "false"}
library(uxr)
```

```{r}
library(uxr)
compare_benchmark_event(benchmark = 0.80,
                        event = 10,
                        total = 12,
                        event_type = "success",
                        notes = "executive")
```

