---
title: "Compare with Benchmarks"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Compare with Benchmarks}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = ''
)
```

The `compare_benchmark_*` functions provide ways to compare benchmark with data like events and times.

## Compare an Event with a Benchmark

**Note**: This function is not yet released. You need to install the development version to use this function. To install the developmental version enter this in your console: `remotes::install_github("joe-chelladurai/uxr")`.

An event is "a thing that happens" (Oxford Learner's Dictionary).

**Example:**

10 out of 14 people successfully completed a task on an interface. What is the probability of success above a benchmark of 80%?

You can use the `compare_benchmark_event()` function to answer this question. This function requires a benchmark value, number of events (in this case successful events), and the total number of events. To pass a `benchmark` value of 80%, you'll need to specify it as 0.8. The `event` and `total` arguments each take numeric values 1 or above.

The function calculates the success rates and returns a cumulative probability value against the benchmark. This probability value indicates the success rate if we were to use this interface with potential users, given a representative sample.

```{r setup, echo = "false"}
library(uxr)
```

```{r}
#| eval: false
compare_benchmark_event(benchmark = 0.80,
                        event = 10,
                        total = 12,
                        event_type = "success",
                        notes = "minimal")
```

```{bash}
#| eval: false

-- Compare Event Rate with a Benchmark---------------------------------------------
Executive: Based on the success rate of 84%, the probability that this rate exceeds
a benchmark of 80% is 44%
  term           result  
  event              10  
  total              12  
  benchmark         80%  
  probability     0.442  

```


## Compare Time with a Benchmark

**Note**: This function is not yet released. You need to install the development version to use this function. To install the developmental version enter this in your console: `remotes::install_github("joe-chelladurai/uxr")`.

**Example:**

7 people successfully took 60, 53, 70, 42, 62, 43, and 81 seconds to complete a task. What is the probability that time taken to complete this task is above a time of 60 seconds?

You can use the `compare_benchmark_time()` function to answer this question. This function requires a benchmark value and a list of times. To pass a `benchmark` value of 60s, you can specify this as 60.

```{r}
#| eval: false
compare_benchmark_time(benchmark = 60,
                       time = c(60, 53, 70, 42, 62, 43, 81),
                       alpha = 0.05)
```

```{bash}
#| eval: false
-- Compare Time with a Benchmark ------------------------------------------------------------
  term          t.result.  
  lower_ci           45.8  
  upper_ci           71.7  
  t                 0.509  
  probability       0.314  
```


## Compare Score with a Benchmark

**Note**: This function is not yet released. You need to install the development version to use this function. To install the developmental version enter this in your console: `remotes::install_github("joe-chelladurai/uxr")`.

```{r}
#| echo: false
t_dist_one_tailed <- function(t_score, degrees_of_freedom) {
  pt(-abs(t_score), degrees_of_freedom)
}
```



```{r}
#| eval: false
data <- 68 + 17 * scale(rnorm(20)) # 68 = mean, 17 = sd
compare_benchmark_score(data, benchmark = 60, alpha = 0.5)
```


```{bash}
#| eval: false
── Compare Score with a Benchmark ──────────────────────────────────────────────────────────────
We can be 98% confident that the true score is between 60 and 76
  term                result  
  mean                    68  
  sd                      17  
  se                3.801316  
  n                       20  
  df                      19  
  alpha                  0.5  
  probability          0.024  
  tail                   one  
  confidence           0.976  
  margin_of_error          8  
  t                    2.105  
  lower_ci                60  
  upper_ci                76  
```


